The benefits of prefetching for large-scale cloud-based neuroimaging analysis workflows

### 2021-10-01 paper/paper.tex
addressing comments

@@

Rolling Prefetch combines prefetching with data eviction. By evicting data post application processing, it ensures a reduced footprint on local storage. Rolling Prefetch consists of three threads: (1) the reading thread loads data blocks from local storage and marks them for eviction, (2) the prefetching thread transfers data blocks from cloud storage to local storage, and (3) the eviction threads deletes the blocks that have been marked for eviction.
% \valerie{cut read alg below}
% \begin{algorithm}
% \SetAlgoLined
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%     \Input{$start$ the start position of the read;\\
%     $end$ the end position of the read;\\}
%     \Output{$output$ the file contents located between $start$ and $end$}

@@

>>>>

Since Rolling Prefetch is implemented as a layer atop \sfs, it can easily replace an existing call to S3Fs by calling \texttt{S3PrefetchFileSystem} instead of \texttt{S3FileSystem}.

@@

Rolling Prefetch combines prefetching with data eviction. By evicting data post application processing, it ensures a reduced footprint on the local storage leveraged as cache by Rolling Prefetch
(e.g. tmpfs, SSD, HDD). Rolling Prefetch consists of three threads: (1) the reading thread loads data blocks from local storage and marks them for eviction, (2) the prefetching thread transfers data blocks from cloud storage to local storage, and (3) the eviction threads deletes the blocks that have been marked for eviction.
% \valerie{cut read alg below}
% \begin{algorithm}
% \SetAlgoLined
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%     \Input{$start$ the start position of the read;\\
%     $end$ the end position of the read;\\}
%     \Output{$output$ the file contents located between $start$ and $end$}

@@

Our results show that significant speedup can be gained even in instances where compute is rather short. While our results
pertain to the applicability of Rolling Prefetch to neuroimaging, similar speedups can be expected from other kinds of sequentially read data processing,
such as a filter on a very large file.
